---
title: "Deliverable #1"
author: "Tony Buranzon"
output:
  html_document:
    df_print: paged
---

First we will need to load a couple R libraries we will need in order to manipulate our data.
```{r}
suppressMessages(library(tidyverse))
```

#### Data Retrieval
First things first, lets read in our datasets. If you haven't downloaded the datasets yet, please do so from my [github](https://github.com/introdsci/DataScience-tonyburanzon).


```{r}
course_meta = read_tsv("./datasets/course-meta.csv")
course = read_tsv("./datasets/courses.csv")
colnames(course_meta)
colnames(course)
```

#### Rename Columns
As we can see the column names of our datasets are pretty well named except for 'catch' which is what they use for timestamp, so we will change that.
```{r}
colnames(course_meta)[colnames(course_meta) == "catch"] = "timestamp"
```

The data is also already pretty well organized and doesn't seem to violate any of the rules of tidy data.Each row contains one sample, each column describes one aspect, and each value has its own cell. We can thank our source for that! Now lets move on and begin to visualize our data a bit. 

Now lets go ahead and take a look at our tidy datasets. 
```{r}
course
course_meta
```

#### Visualization
Here we can see how many of each course was made categorized by difficulty.

```{r}
(plot = ggplot(data=course) + geom_bar(aes(x=course$difficulty), width=.3, fill='blue') 
    + xlab("Difficulty") + ylab("Count"))
```

#### Moving Forward
Moving forward some of the questions I would like to answer is what makes a course a course popular. I plan to answer this by looking into what courses with high amounts of plays have in common. Is there anything specifically that contributes to the likeness of a course being higher than others? As of now, it's hard to say what exactly could lead to this, but I'm guessing who made the course and what difficulty it is will contribute a lot to its likeness.



