---
title: "Super Mario Maker" #replace the title with something short and catchy to represent your project
subtitle: "Tony's Data Science Portfolio" #replace blank with your name
output:
  html_document:
    df_print: paged
---

## Abstract

In a world where online gaming is becoming so popular, I want to analyze how users interact in an environment where other users are the creators. Super Mario Maker is a game where anyone can design a course based on the orignal *Super Mario*. This dataset contains information about the different courses users have created and how players have intereacted with them. Addintionally, I chose this dataset because out of the box, this data is very clean and there is a ton of it. With this much data relating to different aspects of the game, it will surely provide an avenue to discover some interesting connections.

### 1. Discovery and Data Preparation

In this deliverable, we will organize, clean and begin to visualize the data by use of some graphs. The original dataset can be found [here](https://www.kaggle.com/leomauro/smmnet/downloads/smmnet.zip/1#likes.csv).
  

First we will need to load a couple R libraries we will need in order to manipulate our data.
```{r}
suppressMessages(library(tidyverse))
```

####Data Retrieval
First things first, lets read in our datasets. If you haven't downloaded the datasets yet, please do so from my [github](https://github.com/introdsci/DataScience-tonyburanzon).


```{r}
course_meta = read_csv("./datasets/course-meta.csv")
course = read_csv("./datasets/courses.csv")
colnames(course_meta)
colnames(course)
```

####Rename Columns
As we can see the column names of our datasets are pretty well named except for 'catch' which is what they use for timestamp, so we will change that.
```{r}
colnames(course_meta)[colnames(course_meta) == "catch"] = "timestamp"
```

The data is also already pretty well organized and doesn't seem to violate any of the rules of tidy data.Each row contains one sample, each column describes one aspect, and each value has its own cell. We can thank our source for that! Now lets move on and begin to visualize our data a bit. 

####Visualization
Here we can see how many of each course made there are categorized by difficulty.

```{r}
(plot = ggplot(data=course) + geom_bar(aes(x=course$difficulty), width=.3, fill='blue') 
    + xlab("Difficulty") + ylab("Count"))
```




### 2. Model Planning and Building

Coming soon...

### 3. Results and Operationalization

Coming soon...

